Multi-target detection with application to cryo-electron microscopy

### 2019-02-26 inverse_problems/inverse_problems.tex
no message

Autocorrelation analysis can be carried out in dimensions greater than one. In the following experiment, we estimated 
an 50-by-50 pixel image of Einstein with mean zero from a growing number of observations. Each observation is  of size $4096\times 4096$ pixels and contains on average, 700 occurrences  at random locations, while keeping the separation condition~\eqref{eq:spacing}.  
Thus, about 10\% of each micrograph contains signal. The micrographs are contaminated with additive white Gaussian noise with standard deviation $\sigma=3$,  corresponding  to SNR = $\frac{M\|x\|_F^2} {\sigma^2N} \approx1/370$. This high noise level is illustrated in Figure~\ref{fig:micro_example}. 
To simplify the experiment, we assume the number of signal occurrences and the noise standard deviation are known. Micrographs are generated such that any two occurrences are always separated by at least 49 pixels in each direction in accordance with the separation condition~\eqref{eq:spacing}.

@@

\begin{figure}[h]
	\centering
	\includegraphics[width=.8\linewidth]{Einstein_recovery_error_combined}
	\caption{\label{fig:error_per_micro}Relative error curves for the experiment of Figure~\ref{fig:Einst_example}.}
\end{figure}

>>>>

Autocorrelation analysis can be carried out in dimensions greater than one. In the following experiment, we estimated 
an 50-by-50 pixel image of Einstein with mean zero from a growing number of observations. Each observation is  of size $4096\times 4096$ pixels and contains on average, 700 occurrences  at random locations, while keeping the separation condition~\eqref{eq:spacing}.
The micrographs are contaminated with additive white Gaussian noise with standard deviation $\sigma=3$,  corresponding  to SNR = ${\frac{M\|x\|_F^2} {\sigma^2N} \approx1/370}$. This high noise level is illustrated in Figure~\ref{fig:micro_example}. 
As explained in Section~\ref{sec:high_dimensions}, an image is determined uniquely form its second-order autocorrelation.
Hence, to use this property and keep things simple, we assume the number of signal occurrences and the noise standard deviation are known so that we can estimate the second-order autocorrelation of the image from thos the observation directly.  %Micrographs are generated such that any two occurrences are always separated by at least 49 pixels in each direction in accordance with the separation condition~\eqref{eq:spacing}.

@@

%\begin{figure}[h]
%	\centering
%	\includegraphics[width=.8\linewidth]{Einstein_recovery_error_combined}
%	\caption{\label{fig:error_per_micro}Relative error curves for the experiment of Figure~\ref{fig:Einst_example}.}
%\end{figure}
